---
title: "Auto"
author: "Igor Adamiec"
date: "31 maja 2019"
output: html_document
---

https://data.library.virginia.edu/diagnostic-plots/

```{r}
library(ISLR)
library(tidyverse)
```

```{r}
auto <- Auto 
#%>% mutate(origin = as.factor(origin))
```

```{r}
auto %>% summary()
```

```{r}
auto %>% glimpse
```


# a) Use the lm() function to perform a simple linear regression with
# mpg as the response and horsepower as the predictor. Use the
# summary() function to print the results. 

```{r}
model_a <- lm(data = auto, 
              formula = mpg ~ horsepower)
model_a %>% summary
```


Comment on the output.
For example:

##  Is there a relationship between the predictor and the response?

Tak - vartość p jest tak mała, że odrzucamy hipotezę zerową o tym, że współczynniki regresji są równe 0. Potwierdza to duża wartość statystyki F.

```{r}
ggplot(data = auto, aes(x = horsepower, y = mpg)) + geom_point()
```

## How strong is the relationship between the predictor and the response?

residual error relative to the response
```{r}
RSE <- 4.906
mpg_mean <- auto$mpg %>% mean(na.rm = T)
RSE/mpg_mean * 100
```

R^2 = 0.606, czyli horsepower wyjaśnia 60,6% wariancji zmiennej mpg.

## Is the relationship between the predictor and the response
positive or negative?

```{r}
model_a$coefficients
```

Relacja jest negatywna.

## What is the predicted mpg associated with a horsepower of
98? What are the associated 95% confidence and prediction
intervals?

```{r}
predict(model_a, data.frame(horsepower = 98),
        interval = "confidence")
```

```{r}
predict(model_a, data.frame(horsepower = 98),
        interval = "prediction")
```

# Plot the response and the predictor. Use the abline() function
to display the least squares regression line.

```{r}
auto %>% 
  ggplot(aes(x = horsepower)) +
  geom_point(aes(y = mpg)) +
  geom_line(aes(y = model_a$fitted.values), color = "red", size = 2)
```

# Use the plot() function to produce diagnostic plots of the least
squares regression fit. Comment on any problems you see with
the fit.

```{r}
par(mfrow = c(2, 2))
plot(model_a)

```




Residuals - widać jakiś trend - może to być dowód na nieliniowość


```{r}
ggplot(data = auto, aes(x = model_a$fitted.values, y = rstudent(model_a))) + geom_point()
```
Żadna wartość nie jest mniejsa niż -3 lub większa niż 3 - nie ma outlierów

```{r}
ggplot(data = auto, 
       aes(x = hatvalues(model_a),
           y = rstudent(model_a))) +
  geom_point() +
  geom_line(aes(y = 0), linetype = "dashed") + 
  geom_text(aes(label = which.max(hatvalues(model_a)), x = hatvalues(model_a)[116] - .001, y = rstudent(model_a)[116] )) + 
  geom_label(aes(label = which(rstudent(model_a) %in% rstudent(model_a)[rstudent(model_a) > 3 | rstudent(model_a) < -3 ]), x = hatvalues(model_a)[which(rstudent(model_a) %in% rstudent(model_a)[rstudent(model_a) > 3 | rstudent(model_a) < -3 ])] - .001, y =  rstudent(model_a)[rstudent(model_a) > 3 | rstudent(model_a) < -3 ] ))
```

```{r}
rstudent(model_a) %>% which.max()
```

```{r}
hatvalues(model_a)[which(rstudent(model_a) %in% rstudent(model_a)[rstudent(model_a) > 3 | rstudent(model_a) < -3 ])]
which(rstudent(model_a) %in% rstudent(model_a)[rstudent(model_a) > 3 | rstudent(model_a) < -3 ])
```

