---
title: "Auto poly"
author: "Igor Adamiec"
date: "31 maja 2019"
output: html_document
---

```{r}
library(ISLR)
library(GGally)
```


Produce a scatterplot matrix which includes all of the variables
in the data set.

```{r message = FALSE}
auto %>% 
  select(-name) %>% 
  ggpairs()
```

Compute the matrix of correlations between the variables using
the function cor(). You will need to exclude the name variable, 
which is qualitative.

```{r}
auto %>% select(-name) %>% cor()

```

Use the lm() function to perform a multiple linear regression
with mpg as the response and all other variables except name as
the predictors. Use the summary() function to print the results.

```{r}
model_multi <- lm(data = auto,
                  formula = mpg~. - name)
model_multi %>% summary
```

Is there a relationship between the predictors and the response?

F statistics jest daleka od 1m a p value jest małe - jest zależność.

Which predictors appear to have a statistically significant
relationship to the response?

wszystkie z P value < 0,05

What does the coefficient for the year variable suggest?

Przy pozostałYch zmiennych stałych, mpg zwiększa sięo 0,751 z każ•dym rokiem produkcji

Use the plot() function to produce diagnostic plots of the linear
regression fit. Comment on any problems you see with the fit.
Do the residual plots suggest any unusually large outliers? Does
the leverage plot identify any observations with unusually high
leverage?

```{r}
plot(model_multi)
```

wydaje się być zależność nieliniowa, 
punkt 14 wydaje się mieć duży leverage

```{r}
plot(predict(model_multi), rstudent(model_multi))
```

Na pewno są outliery

Use the * and : symbols to fit linear regression models with
interaction effects. Do any interactions appear to be statistically
significant?

```{r}
lm(data = auto, mpg~cylinders*displacement+displacement*weight) %>% 
summary()
```

Wziąłem 2 najbardziej skorelowane pary i sprawdziłem ich interakcje - displacement:weight jest statystycznie istotna, a cylinders:displacement - nie (tak jak samo)

```{r}
lm(data = auto, mpg~displacement*weight) %>% 
summary()
```


Try a few different transformations of the variables, such as
log(X),
√
X, X2. Comment on your findings.


